---
title: "ndex"
author: "Alex"
date: "9/12/2022"
# output: html_document
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PFOCR NDEx update
This R notebooks updates the ndex field in the frontmatter of pathway figure md files based on updates to a tsv mapping file. 
 
```{r install, include=FALSE}
library(tidyr)
library(dplyr)
library(magrittr)
library(tools)
library(yaml)
```

## Update mapping file via NDEx API
Run this after new uploads to NDEx in order to update the local mapping file. 
***Do not include this chunk in the GitHub action (use eval=FALSE).***
***This chunk can take ~3 hours to run!***
```{r ndex-api, eval=FALSE}
library(RJSONIO)
library(httr)
library(utils)

get.networkset <- "http://www.ndexbio.org/v2/networkset/85034b42-de8a-11ea-99da-0ac135e8bacf"
res <- GET(url=URLencode(get.networkset))
res.char <- rawToChar(res$content)
res.json <- RJSONIO::fromJSON(res.char)
pfocr.ndex <- res.json$networks

for(i in seq(1, length(pfocr.ndex), by=10)){ # ten at a time, write as we go
  pfocr.ndex.sub <- pfocr.ndex[i:(i+9)]
  pfocr.figid <- unlist(lapply(pfocr.ndex.sub, function(n){
    if (!is.na(n)){
      get.summary <- paste("http://www.ndexbio.org/v2/network",n,"summary", sep = "/")
      res <- GET(url=URLencode(get.summary))
      res.char <- rawToChar(res$content)
      res.json <- RJSONIO::fromJSON(res.char)
      figid <- res.json$properties[[10]]$value
      tools::file_path_sans_ext(figid)
    }
  }))
  ndex.figid.df <- data.frame(pfocr.figid, pfocr.ndex.sub)
  write.table(ndex.figid.df, "../_data/ndex_map.tsv", sep = "\t",
              row.names = F, col.names = F, quote = F, append = T) #APPEND
  Sys.sleep(2) # give ndex api a break
}
```

## Update md files
This chunk should be run as part of a GitHub action triggerd by changes to the mapping tsv file.
```{r update}

```